Software Citation Principles

### 2016-04-19 sc-principles/software-citation-principles.tex
edits to final section

Software citation principles without clear worked-through examples are of
limited value to potential implementers and so in addition to the principles
document the final deliverable of this working group will be an implementation
paper outlining working examples for each of the use cases listed in ~\S\ref{sec:use_cases}.

Following on from these efforts, a new Force11 working group is expected to
begin with the goal of supporting potential implementers of the software citation
principles as well as developing potential metadata standards.

>>>>

Software citation principles without clear worked-through examples are of
limited value to potential implementers, and so in addition to this principles
document the final deliverable of this working group will be an implementation
paper outlining working examples for each of the use cases listed in ~\S\ref{sec:use_cases}.
Following these efforts, a new FORCE11 working group is expected to
begin with the goal of supporting potential implementers of the software citation
principles as well as developing potential metadata standards.
